### 2014-08-31 fundamentals/intro.tex
makes an image directory for images
edits motivation section for conciseness

Methods for calculating those metrics vary among simulators. Some model the fuel cycle at static equillibrium, while others 
capture fuel cycle dynamics.  Similarly, while some simulators discretely model 
material and and facilities, others track streams of materials and 
fleets of facilities in an aggregated fashion. Depending on their intended use, 
simulators often model some aspect of the fuel cycle in great detail. For this 
reason, simulators specialize in economics, material isotopics, or 
transmutation detail, where others do not.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}, while universities and industry have 
simultaneously developed tools of their own as well, such as 
\gls{CAFCA}\cite{guerin_benchmark_2006}.

The \Cyclus code arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.

@@

% MJG - @gonuke has always cited method-to-method comparisons as the primary
% benefit \Cyclus can bring to the table. Do we want to frame the hero narrative
% in that context? The more I think about, the more I feel like this is a
% secondary argument. I'll take a crack at a few sentences below.

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables two major capabilites that previous 
simulators were lacking. First, it enables simulations at multiple levels of 
fidelity. Second, it facilitates direct comparison of modeling methodologies.

% MJG - I don't claim that all of this belongs in the beginning of this
% subsection, but here's some more content.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics{modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully 
closed collaborations.}
\label{fig:modifiedopen}
\end{figure}

@@

ABM is modern, sophisticated, true to reality, and it takes advantage of modern
computing resources. Furthermore, agent-based modeling provides an analyst a
more natural perspective from which to model a given problem. In the nuclear
fuel cycle context for example, an analyst can design an agent with
reactor-related logic and a separate agent with fuel fabrication-related logic.

System dynamics popular approach for modeling nuclear fuel cycles in current
tools (cite VISION/CAFCA). It has been shown in the literature
\cite{macal_agent-based_2010} that any system dynamics model can be translated
into an agent-based model. Furthermore, it has been shown that agent-based
techniques can provide a richer model than can system dynamics. Formally, the
set of system dynamics models is a strict subset of agent-based models.

>>>>

Methods for calculating those metrics vary among simulators. Some model the 
fuel cycle at static equillibrium, while others capture fuel cycle dynamics.  
Similarly, while some simulators discretely model material and and facilities, 
others track streams of materials and fleets of facilities in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail. For this reason, 
some simulators specialize in economics, material isotopics, or transmutation 
detail, where others do not.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}, while universities and industry have 
simultaneously developed tools of their own as well, such as 
\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.

The \Cyclus simulator arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios. \Cyclus is a dynamic 
simulator that treats both materials and facilities discretely, with an 
architecture that permits simulations with multiple and variable levels of 
fidelity.

@@

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables major capabilites that previous 
simulators lack. First, its \emph{modular and open architecture}  
facilitates targeted contribution 
and collaboration within the nuclear fuel cycle analysis community. 
Additionally, \emph{agent interchangability} facilitates direct comparison of modeling 
methodologies. Finally, the flexibility and generality of its \emph{\gls{ABM}} 
paradigm and \emph{discrete, object-oriented approach} emphasizes applicability of the \Cyclus tool accross a broader range 
of applications than other simulators.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics{./images/modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully 
closed collaborations.}
\label{fig:modifiedopen}
\end{figure}

@@

\gls{ABM} is modern, sophisticated, true to reality, and it takes advantage of modern
computing resources. Furthermore, agent-based modeling provides an analyst a
more natural perspective from which to model a given problem. In the nuclear
fuel cycle context for example, an analyst can design an agent with
reactor-related logic and a separate agent with fuel fabrication-related logic.

System dynamics popular approach for modeling nuclear fuel cycles in current
tools \cite{VISION,CAFCA}. It has been shown in the literature
\cite{macal_agent-based_2010} that any system dynamics model can be translated
into an agent-based model. Furthermore, it has been shown that agent-based
techniques can provide a richer model than can system dynamics. Formally, the
set of system dynamics models is a strict subset of agent-based models.
